VIPRE: Virtualized Intermittently-Powered Runtime Environment

### 2017-07-11 paper/background.tex
Expanding background section

Many platforms already enable intermittent computation: WISP~\cite{} (with its variants such as WISPCam~\cite{}), Moo~\cite{moo}, ambient backscatter~\cite{liu_sigcomm_2013}, or computation RFID commercial platforms such as~\cite{}. In case of the above platforms, the main source of energy is electromagnetic radiation in the radio frequency range. Naturally, other forms of energy harvesting exist, The reader is refered to extensive surveys~\cite{}.

Application include long-term battery-less monitoring. One example is the distributed monitoring of moisture of large plant fields during vegetation~\cite{}. Other applications include battery-less image capture and processing~\cite{}, distributed low-power networking~\cite{} or implantable sensors~\cite{rodriguez_tbcs_2015}.

Energy provided from the ambient is not stable and difficult to predict accurately. Combined with the fact that energy supply is small, there is little leeway to store enough of energy to guarantee prolonged periods of computation. Energy breaks happen every hundred of ms~\cite{}.

>>>>

Many platforms already enable intermittent computation: WISP~\cite{wisp5} (with its variants such as WISPCam~\cite{naderiparizi_rfid_2015} or NeuralWISP~\cite{holleman_biocas_2008}), Moo~\cite{moo}, ambient backscatter~\cite{liu_sigcomm_2013}, or commercial computation RFID platforms such as~\cite{medusa_farsens_2017}. In case of the above platforms, the main source of energy is electromagnetic radiation in the radio frequency range. Naturally, other forms of energy harvesting sources exist: temperature gradient, light/sun radiation, vibrations, (micro-)motions, fluid flow or body fluids (blood, gastric acid). The reader is referred to example extensive surveys discussing energy harvesting for low-power embedded systems in detail~\cite{paradiso_pvc_2005,soyata_csm_2016,prasad_comst_2014,ku_cst_2016}.

Application include long-term battery-less monitoring. One example is the distributed monitoring of moisture of large plant fields during vegetation~\cite{}. Other applications include battery-less image capture and processing~\cite{naderiparizi_rfid_2015}, distributed low-power networking~\cite{}, insect monitoring~\cite{thomas_jbcs_2012} or implantable sensors~\cite{rodriguez_tbcs_2015}.

Energy provided from the ambient is not stable and difficult to predict accurately. Combined with the fact that energy supply is small, there is little leeway to store enough of energy to guarantee prolonged periods of computation. Energy breaks happen every hundred of ms~\cite{soyata_csm_2016,}.
